\section{Experiences}

\cventry{Aug 2023--Present}{DevOps Engineer}{GanjeHost}{Tehran, Iran}{}{
    \begin{itemize}
        \item Spearheaded the installation, maintenance, and support of \textbf{vSphere clusters and ESXi servers}, 
        including \textbf{High-Availability pfSense nodes} for traffic management and monitoring across shared hosting servers.
        \item Automated deployment and configuration of shared hosting environments using \textbf{Bash} and \textbf{Ansible}, 
        significantly improving operational efficiency and reducing setup time.
        \item Implemented end-to-end service monitoring solutions with \textbf{Prometheus}, \textbf{Grafana}, and \textbf{Zabbix}, 
        enabling proactive infrastructure management and issue resolution.
        \item Established and maintained \textbf{KVM virtualization clusters}, 
        optimizing resource utilization and enhancing the performance of virtualized systems.
        \item Designed and deployed comprehensive \textbf{network infrastructure} and \textbf{data center layouts}, 
        managing \textbf{physical network equipment} including MikroTik routers and Cisco switches to deliver a redundant, 
        highly available network for the vSphere cluster.
        \item Managed and maintained \textbf{HPE server hardware and software}, ensuring consistent performance and reliability of critical infrastructure.
    \end{itemize}
}

\cventry{Dec 2024--Present}{DevOps Engineer}{Webito}{Yerevan, Armenia}{}{
    \begin{itemize}
        \item Managed and optimized \textbf{ESXi/vSphere servers}, including OS upgrades, resource tuning, and ongoing maintenance.
        \item Built and maintained CI/CD pipelines for developers, streamlining deployment workflows and improving delivery speed.
        \item Designed and implemented \textbf{backup strategies} for critical services, ensuring data reliability and rapid recovery.
        \item Containerized multiple services and maintained their infrastructure, improving scalability and operational consistency.
        \item Deployed and maintained \textbf{monitoring solutions} to ensure service reliability and proactive issue detection.
        \item Advised on \textbf{cloud architecture} and provided migration consulting to improve performance and reduce operational overhead.
    \end{itemize}
}